---
title: "IS 606 - Project 1"
author: "H. Berk, S. Hong, R. Srinivasan, J. Hamski"
date: "March 4, 2015"
output: html_document
---
***
The goal of the project is to determine how many sandwiches of each type a sandwich shop prorietor (James) should bring each day in order to maximize his expected profits. There are two datasets:  
1. The daily sales data contains number brought and number demanded for each sandwich.   
2. The pricing data contains the cost and sale price of each type of sandwich.

```{r}
details <- read.csv("details.csv", header = TRUE)
sales <- read.csv("sales.csv", header = TRUE)

profit.margin <- details$price - details$cost

ham.revenue <- sales$demand.ham * 6.5
turkey.revenue <- sales$demand.turkey * 6.5
veggie.revenue <- sales$demand.veggie * 5.0

ham.cost <- sales$available.ham * 3.5
turkey.cost <- sales$available.turkey * 4.0
veggie.cost <- sales$available.veggie * 2.5

distrham <- table(sales$demand.ham)/length(sales$demand.ham)
distrturkey <- table(sales$demand.turkey)/length(sales$demand.turkey)
distrveggie <- table(sales$demand.veggie)/length(sales$demand.veggie)
```

The distribution of ham sales is:

```{r, echo=FALSE}
plot(distrham)
```