---
title: "IS 606 - Project 1"
author: "H. Berk, S. Hong, R. Srinivasan, J. Hamski"
date: "March 4, 2015"
output: html_document
---
***
**Report For: James's Sandwich Stand**

Per our group consulting services agreement, please find this quantitative analysis on sandwich stand operations and inventory control for James's Sandwich Stand below. The goal of this report is to determine how many sandwiches of each type James's Sandwich Stand should bring each day in order to maximize expected profits. 

Our consulting group was provided with two datasets:  
1. The daily sales data, containing the number brought and number demanded for each sandwich over 130 days   
2. Pricing data, containing the cost and sale price of each type of sandwich

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
library(knitr)
details <- read.csv("details.csv", header = TRUE)
sales <- read.csv("sales.csv", header = TRUE)
```
```{r}
profit.margin <- details$price - details$cost

ham.revenue <- sales$demand.ham * 6.5
turkey.revenue <- sales$demand.turkey * 6.5
veggie.revenue <- sales$demand.veggie * 5.0

ham.cost <- sales$available.ham * 3.5
turkey.cost <- sales$available.turkey * 4.0
veggie.cost <- sales$available.veggie * 2.5

distrham <- table(sales$demand.ham)/length(sales$demand.ham)
distrturkey <- table(sales$demand.turkey)/length(sales$demand.turkey)
distrveggie <- table(sales$demand.veggie)/length(sales$demand.veggie)
```
The distribution of ham, turkey, and veggie sales are:
```{r, echo=FALSE}
plot(distrham)
plot(distrturkey)
plot(distrveggie)
```

The average daily proft for each sandwich is below. 
```{r}
profit.ham <- ham.revenue - ham.cost
profit.turkey <- turkey.revenue - veggie.cost
profit.veggie <- veggie.revenue - veggie.cost
average.profit <-c(mean(profit.ham), mean(profit.turkey), mean(profit.veggie))
average.profit <- as.data.frame(average.profit, row.names = c('ham', 'turkey', 'veggie'))
kable(average.profit)
```

We can model profit using a Poisson distribution. 
For each sandwich type, we assign:
x = number of sandwiches sold 
Y = profit
p.Margin = profit margin for each sandwich
λ = average no. of sandwiches sold per day

For Ham:
```{r}
lambda <- mean(sales$demand.ham)
p.Margin <- 3


```

